---
title: "Factors Influencing Adult Obesity in the United States"
author: "Maha Gasim, Amal Ahmed, Arnela Halili"
date: "2024 course project — portfolio refactor"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
source("../R/00_packages.R")
source("../R/01_prepare_data.R")
source("../R/02_descriptive_analysis.R")
source("../R/03_models.R")
```

# Research question

Which demographic, socioeconomic, behavioral, and health characteristics are associated with adult obesity in the United States, and how much does baseline obesity risk vary across states?

# Data

The analysis uses the 2022 BRFSS reduced to the variables documented in `stata/01_extract_brfss.do`. Raw data are not versioned in the repository; see `data/README.md`.

```{r load-data}
data <- load_analysis_data()
dim(data)
```

# Exploratory analysis

```{r descriptives}
descriptives <- run_descriptives(data, "../results")
head(descriptives$obesity_by_state, 10)
descriptives$conditional_sex
```

# Regression models

```{r models}
models <- fit_obesity_models(data, "../results")
summary(models$age_logit)
summary(models$multivariable_logit)
models$ordinal_comparison
summary(models$state_glmm)
```

# Interpretation and scope

The original course project compared binary, multinomial, ordinal, and mixed-effects logistic specifications. The portfolio refactor preserves that modelling scope and makes the data transformations and model formulas explicit. The original analysis did not implement survey-weighted estimation, so the results here should be read as a reproduction of the course workflow rather than population-representative BRFSS estimates.
